Automated verification of electrical systems: literature review and case studies of stand-alone solar photovoltaics\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2019-04-06 Tex/CAV2019/Trindade_Cordeiro_CAV2019.tex
new text

Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}. Progress has been made worldwide; in particular, the number of people without electricity access fell below 1 billion threshold for the first time in 2017~\cite{IEAweo2018}. In order to provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed; \textcolor{red}{This sentence is unclear... what is the ``role to play''?} however, that grid extension will still have a role to play, especially in urban areas~\cite{IEAweo2018}.

@@

The conversion of traditional power grid into a smart grid, a fundamental example of a Cyber-Physical System (CPS), raises a number of issues that requires novel methods and applications. In 2012, a Chinese smart grid implementation was considered as case study to address the verification problem for performance and energy consumption~\cite{Yukseletall2012}. The authors employed a stochastic model checking approach and presented a modelling and analysis study using PRISM~\cite{KwiatkowskaNP11}. The focus of this study was on how CPs integrate information and communication technology functions to the physical elements of a system for monitoring and controlling purposes; here the authors employed automated verification of certain quantitative properties of the system \textcolor{red}{for example?}. %, with no interest in power generation or even solar PV systems.

@@

\textcolor{red}{We have to reduce this paragraph:} In 2017, Abate suggested the application of formal methods to verify and control the behavior of computational devices interacting over a shared and smart infrastructure~\cite{Abate2017}. He has shown that formal techniques can provide compelling solutions not only when safety-critical goals are the target, but also to tackle verification and synthesis problems on populations of such devices. This study also argued that alternative solutions based on classical analytical techniques or on approximate computations are prone to errors with global repercussions. Two different areas were identified: thermal loads and electricity-generating devices interacting over a smart energy network or over a local power grid. Abate discussed the aggregation of large populations of thermostatically-controlled loads and of PV panels, and the corresponding problems of energy management in smart buildings, of demand-response on smart grids, and respectively of frequency stabilization and grid robustness. The focus is on controlling the behavior of components, thereby verifying the smart grid as a ``system of systems'' within the context of ``internet of things''. The author also uses approximate model checking of stochastic and hybrid models.

@@

Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw. Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored, and questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}. Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}. Here we evaluate three state-of-the-art model checkers to formally verifying PV desgins w.r.t. user requirements.

@@

Ultimate Automizer is an automatic software verification tool for C programs that is able to check safety and liveness properties. The tool implements an automata-based instance of the Counterexample-Guides Abstraction Refinement  (CEGAR) scheme. CEGAR is a technique that iteratively refines an abstract model using counterexamples and use three concepts: precision, feasibility check and refinement~\cite{CEGAR}. In each iteration, Automizer picks a trace (sequence of statements) that leads from the initial location to the error location and check whether the trace is feasible or infeasible. If the trace is feasible, an error is reported to the user; otherwise it is computed a sequence of predicates along the trace as a proof of the trace's infeasibility. The predicates are a sequence of interpolants since each predicate Äú``interpolates''Äù between a set of reachable states and a set of states from which it cannot reach the error. In the refinement step of the CEGAR loop, Automizer tries to find all traces whose infeasibility can be shown with the given predicates and subtract these traces from the set of (potentially spurious) error traces that have not yet been analyzed. It is used automata to represent sets of traces. The difference to a classical CEGAR-based predicate abstraction is that Automizer has to do any logical reasoning (e.g., SMT solver calls) that involves predicates of different CEGAR iterations~\cite{Automizer2018}.

@@

The mathematical modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}. %It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity. In Fig.\ref{fig:blockdiagram}, there are two variables that depend on the site where the system is deployed and the weather (i.e., solar irradiance $G$ and temperature $T$). For night hours or rainy days, we need to hold batteries where power can be stored and used. The use of battery as a storage form implies the presence of a charge controller~\cite{Hansen}. The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required. That converter is called of inverter; and the AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
\begin{figure}[h]
\includegraphics[width=0.6\textwidth]{blockdiagramPVS2}
\centering
\caption{Block diagram for a typical stand-alone PV system~\cite{Hansen}.}
\label{fig:blockdiagram} 
\end{figure}
A wide variety of models exists for estimation of power output of PV modules (and $I-V$ or $P-V$ curves) \textcolor{red}{add citations here}. However, this study will rely on the simplified model of 1-diode since prior work previously demonstrated that this model has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}; the employed model uses formulas from different sources available in the literature~\cite{Hansen,Ross,Saloux}.

@@

Concerning the high-end configuration: (i) verification engine ESBMC, version v5.1.0 was used with the SMT solver Boolector version 2.4.1~\cite{Brummayer}\footnote{\$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-boolector}; (ii) verification engine CBMC 5.6 and MiniSat \textcolor{red}{which version of minisat?}~\cite{Kroening}\footnote{\$ cbmc filename.c --unwind 300}; (iii) Ultimate Automizer version 0.1.24~\cite{Automizer2018}\footnote{\$ ./Ultimate -tc config/AutomizerReach.xml -i filename.c}.

@@

ESBMC and ESBMC Incremental indicated that the $1,200$W system (House 5) has sizing error related to the \textcolor{red}{right?} number of solar panels. Related to the 700W systems (Houses 1-4), ESBMC and ESBMC incremental indicated that there is a situation of low state of charge from batteries that will cause the cut of the load, just after the 16:00h of the day, when the weather condition was not enough to charge the batteries.

>>>>

Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}. Progress has been made worldwide; in particular, the number of people without electricity access fell below 1 billion threshold for the first time in 2017~\cite{IEAweo2018}. In order to provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed; and grid extension will be the standard especially in urban areas~\cite{IEAweo2018}.

@@

The conversion of traditional power grid into a smart grid, a fundamental example of a Cyber-Physical System (CPS), raises a number of issues that requires novel methods and applications. In 2012, a Chinese smart grid implementation was considered as case study to address the verification problem for performance and energy consumption~\cite{Yukseletall2012}. The authors employed a stochastic model checking approach and presented a modelling and analysis study using PRISM~\cite{KwiatkowskaNP11}. The focus of this study was on how CPs integrate information and communication technology functions to the physical elements of a system for monitoring and controlling purposes; here the authors employed automated verification of certain quantitative properties of the system, as 	probability	of	node	failure	in	the	long run, impact	of	repair	service	on	the	failure	risk, and expected energy consumption. %, with no interest in power generation or even solar PV systems.

@@

In 2017, a researcher suggested the application of formal methods to verify and control the behavior of computational devices interacting over a shared and smart infrastructure~\cite{Abate2017}. The author discussed the aggregation of large populations of thermostatically-controlled loads and of PV panels, and the corresponding problems of energy management in smart buildings, of demand-response on smart grids, and respectively of frequency stabilization and grid robustness. The focus was on controlling the behavior of components, thereby verifying the smart grid as a ``system of systems'' within the context of ``internet of things''. The author used approximate model checking of stochastic and hybrid models.

@@

Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw. Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored, and questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}. Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}. Here we evaluate three state-of-the-art model checkers to formally verifying PV designs w.r.t. user requirements.

@@

Ultimate Automizer is an automatic software verification tool for C programs that is able to check safety and liveness properties. The tool implements an automata-based instance of the Counterexample-Guides Abstraction Refinement  (CEGAR) scheme. CEGAR is a technique that iteratively refines an abstract model using counterexamples and use three concepts: precision, feasibility check and refinement~\cite{CEGAR}. In each iteration, Automizer picks a trace (sequence of statements) that leads from the initial location to the error location and check whether the trace is feasible or infeasible. If the trace is feasible, an error is reported to the user; otherwise it is computed a sequence of predicates along the trace as a proof of the trace's infeasibility. The predicates are a sequence of interpolants since each predicate ????? ``interpolates'' ??? between a set of reachable states and a set of states from which it cannot reach the error. In the refinement step of the CEGAR loop, Automizer tries to find all traces whose infeasibility can be shown with the given predicates and subtract these traces from the set of (potentially spurious) error traces that have not yet been analyzed. It is used automata to represent sets of traces. The difference to a classical CEGAR-based predicate abstraction is that Automizer has to do any logical reasoning (e.g., SMT solver calls) that involves predicates of different CEGAR iterations~\cite{Automizer2018}.

@@

The mathematical modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}. %It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity. In Fig.\ref{fig:blockdiagram}, there are two variables that depend on the site where the system is deployed and the weather (i.e., solar irradiance $G$ and temperature $T$). For night hours or rainy days, we need to hold batteries where power can be stored and used. The use of battery as a storage form implies the presence of a charge controller~\cite{Hansen}. The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required. That converter is called of inverter; and the AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
\begin{figure}[h]
\includegraphics[width=0.6\textwidth]{blockdiagramPVS2}
\centering
\caption{Block diagram for a typical stand-alone PV system~\cite{Hansen}.}
\label{fig:blockdiagram} 
\end{figure}
A wide variety of models exists for estimation of power output of PV modules (and $I-V$ or $P-V$ curves)~\cite{Hansen}, \cite{Ross}, \cite{Saloux}. However, this study will rely on the simplified model of 1-diode since prior work previously demonstrated that this model has a small error rate, between 0.03\% and 4.68\% from selected PV panels tested~\cite{Saloux}; the employed model uses formulas from different sources available in the literature~\cite{Hansen,Ross,Saloux}.

@@

Concerning the high-end configuration: (i) verification engine ESBMC, version v5.1.0 was used with the SMT solver Boolector version 2.4.1~\cite{Brummayer}\footnote{\$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-boolector}; (ii) verification engine CBMC 5.6 and MiniSat 2.2.1~\cite{Kroening}\footnote{\$ cbmc filename.c --unwind 300}; (iii) Ultimate Automizer version 0.1.24~\cite{Automizer2018}\footnote{\$ ./Ultimate -tc config/AutomizerReach.xml -i filename.c}.

@@

ESBMC and ESBMC Incremental indicated that the $1,200$W system (House 5) has sizing error related to the right number of solar panels. Related to the 700W systems (Houses 1-4), ESBMC and ESBMC incremental indicated that there is a situation of low state of charge from batteries that will cause the cut of the load, just after the 16:00h of the day, when the weather condition was not enough to charge the batteries.
